A systematic search for transiting planets in the \KT\ data

### 2015-02-15 ms.tex
removing cruft
words about single transits

% \dfmtodo{Didn't Charbonneau show some K2 planet at NYU?  Is that in our list
% and does it need to be mentioned or discussed?  Also, what about the planet we
% were shown by Vandenburg, private communication?}

% (Note: C1 data came out the week between Christmas and New Years, so Charbonneau
% didn't show anything from C1. Based on when he came down to visit you guys, it was
% very likely Andrew's HIP 116454 he showed).

% That's correct. Everyone except for Hogg knows that so I don't think that we
% need to say anything here :-)

@@

We have searched the \KT\ Campaign~1 data set for exoplanet transit signals.
Our search is novel because it includes a very flexible systematics model,
which is fit simultaneously with the exoplanet signals of interest (and
marginalized out).
By this method, we find \dfmtodo{XXXX} new exoplanets, which we have vetted by \dfmtodo{ZZZZ}
method and characterized by probabilistic modeling.
The candidates are listed in \dfmtodo{some table} and
posterior distributions of planet candidate properties are available at
\dfmtodo{thisurl}.

@@

The posterior distributions we release are given in terms of observational
quantities (rather than physical quantities) and are specifically \emph{NOT}
marginalized over stellar properties.
In this work, we are agnostic about fundamental properties of the host stars.
The only assumptions we make are that the star targeted by the \KT\
team is truly the planet host, and that there is no dilution by other stars in
any aperture.
As a result, these posterior distributions reflect the maximum possible
uncertainty in parameters such as the planet radius, which depend sensitively
on properties of the host star.

\dfmtodo{
To use these distributions to characterize the properties of specific systems,
one should weight our samples by inferred stellar properties...
Perhaps give a specific example here with some detailed discussion or math.
}

This is not the last time the \KT\ data will be searched!
There are many heuristic choices and short-cuts made in this search.
For example, the choice to work at 150 principal components is a choice
driven more by computational feasibility than any model selection or
utility optimization.
The systematics model is good for spacecraft-induced variability, but not
intrinsic stellar variability.
The systematics model has no concept of a physical model of the spacecraft or
the camera; that is, it makes little use of our prior information about how
\KT\ images are generated physically.
The search is performed with a box model and severe approximations are employed
to make it fast.
We don't consider planets (which must be abundant) on periods longer
than those that would leave two transits within the \KT\ Campaign~1
data set.

@@

>>>>

@@

We have searched the \KT\ Campaign~1 data set for exoplanet transit signals.
Our search is novel because it includes a very flexible systematics model,
which is fit simultaneously with the exoplanet signals of interest (and
marginalized out).
By this method, we find 38 transiting exoplanets, which we have vetted by both
automatically and manually and characterized by probabilistic modeling.
The candidates are listed in \tab{cand} and posterior distributions of planet
candidate properties are available at \dfmtodo{thisurl}.

@@

In this work, we are agnostic about fundamental properties of the host stars.
The only assumptions we make are that the star targeted by the \KT\
team is truly the planet host, and that there is no dilution by other stars in
any aperture.
As a result, these posterior distributions reflect the maximum possible
uncertainty in parameters such as the planet radius, which depend sensitively
on properties of the host star.
To use these distributions to characterize the properties of specific systems,
one could re-weight our samples using a measurement of the inferred stellar
properties.
\dfmtodo{For example, let's do the Crossfield planets here. The results are
consistent. Boom.}

This project does not live in isolation and this is certainly not the last
time the \KT\ data will be searched!
There are other teams searching the \KT\ light curves for transiting planets
(A.~Vanderburg, private comm.) and they are likely to find some planets that
we did not and vice versa.
We make many heuristic choices and short-cuts in this search.
For example, the choice to work at 150 principal components was based on
computational feasibility and qualitative tests on a handful of light curves
instead of any real model selection or utility optimization.

Another major limitation is that, in principle, the systematics model is
designed to describe spacecraft-induced trends, but not intrinsic stellar
variability.
In practice, the method can still find planets around variable stars but a
more sophisticated model should be more robust in this case.
One appealing option would be to model the systematics as a Gaussian Process
where the input parameters are both time and the same 150 ELCs.
Interestingly, while this model isn't linear, the search and marginalization
can still be executed efficiently---using optimized linear algebra algorithms
\citep{fastgp}---inside the search loop.

@@

The catalog of planet candidates presented here includes only planets with
periods longer than 4 days and at least two transits in the \KT\ Campaign~1
footprint.
This means that we are necessarily missing many planets with orbital periods
outside  this range.
In particular, planets with a single transit in the dataset must be
abundant.
These candidates are the most relevant for the study of planetary system
formation and for statistical inference of the distribution of habitable zone
exoplanets.
What's more, given the observing strategy for \tess, where each field will
only be contiguously observed for one month at a time, methods for finding and
characterizing planets with a single transit are vital and the new \KT\ light
curves are a perfect test bed.
